---
title: "Introduction to habCluster"
output: rmarkdown::html_vignette
# output: pdf_document
vignette: >
  %\VignetteIndexEntry{Introduction to habCluster}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Example

This is a basic example which shows you how to find the cluster of lands:

```{r example, message=FALSE, warning=FALSE, paged.print=TRUE}
library(raster)
library(habCluster)
```

Read in habitat suitability index (HSI) data of wolf in Europe. The HSI values of the cells in the raster indicate how smoothly the wolfs can moved in the cells, and can be used to represent the connection between cells as habitat.
```{r read_data}
hsi.file = system.file("extdata","wolf3_int.tif",package="habCluster")
wolf = raster(hsi.file)
```

Find habitat cluster using Leiden Algorithm. Raster for habitat suitability will be resampled to 40 km (40000m), to reduce calculation amount. Set cluster_resolution_parameter to 0.02 to control the cluster size.

```{r compute}
clst = cluster(wolf, method = cluster_leiden, res = 40000, rp = 0.02, silent = FALSE)
```

You can also embed plots, for example:

```{r cluster, echo=TRUE}
image(wolf, col = terrain.colors(100,rev = T), asp = 1)
plot(clst$boundary, add = T, asp = 1, border = "lightseagreen")
```

## How to Cite
Zhang, C., Q. Dai*, et al, (in review). Identifying Geographical Boundary among Intraspecific Units Using Community Detection Algorithm.
